Pillar 1 - Sequential Pattern Mining

### 2019-02-26 Pillar 1 - Sequential Pattern Mining.Rmd

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
edit_rules <- function(rules){

@@

```{r edit rules}
AR <- lapply(
  X   = AR,
  FUN = edit_rules
  )

SR <- lapply(
  X   = SR,
  FUN = edit_rules
  )
```

```{r}
save(
  AR, SR,
  file = "App/rules/rules.RDATA"
  )
```

@@

```{r}
filter_rules <- function(rules){

@@

    filter(
       count      >= 10,
       lift       >= 1,
       confidence >= 0.4
      )
}
```

```{r}
AR <- lapply(
  X   = AR,
  FUN = filter_rules
  )

SR <- lapply(
  X   = SR,
  FUN = filter_rules
  )
```

```{r save rules, include = FALSE}
save(
  AR, SR,
  file = "App/Recommender System/rules.RDATA"
  )
```

>>>>

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
edit_rules_rulesApp <- function(rules){

@@

```{r edit rules}
AR_rulesAPP <- lapply(
  X   = AR,
  FUN = edit_rules_rulesApp
  )

SR_rulesAPP <- lapply(
  X   = SR,
  FUN = edit_rules_rulesApp
  )
```

```{r}
save(
  AR_rulesAPP, SR_rulesAPP,
  file = "App/rules/rules.RDATA"
  )
```

@@

```{r}
edit_rules_RSAPP <- function(rules){

@@

    filter(
       count      >= 10,
       lift       >= 1,
       confidence >= 0.4
      )

```{r}
AR_RSAPP <- lapply(
  X   = AR,
  FUN = edit_rules_RSAPP
  )

SR_RSAPP <- lapply(
  X   = SR,
  FUN = edit_rules_RSAPP
  )
```

```{r save rules, include = FALSE}
save(
  AR_RSAPP, SR_RSAPP,
  file = "App/Recommender System/rules.RDATA"
  )
```
